miniKanren with fair search strategies

### 2019-05-05 Paper/paper.tex
logical \tt{or}

The syntax of a programming language should reflect its semantics. When writing 
a \conde{} expression in miniKanren, a programmer would expect all clauses 
share the same chance of being explored, as these clauses are written in 
parallel. The existing search strategy, interleaving \DFSi{}, 
however, prioritize its clauses by the order how they are written down. 
Similarly, when a \conde{} is followed by another goal conjunctively, a 
programmer would expect answers in parallel share the same chance of being 
explored. Again, the answers by DFS$_\textrm{i}$ is different from the 
expectation. We have devised three new search strategies that have different 
level of fairness in \disj{} and \conj{}.

@@

\conde intuitively corresponds to \texttt{or} in logic. And thus an unsuspicious
beginner would expect each letter to contribute equally to the result, as
following.

@@

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
A \emph{state} is a collection of constraints. Every answer given by 
miniKanren corresponds to a state. A \emph{search space} is a collection of 
states. And a \emph{goal} is a function from a state to a search space. Goals 
check their input states and outputs possibly extended states. A goal might fail 
for some inputs, in which case the output search space would be empty.

@@

A more interesting situation is when the first conjunctive goal produces 
infinite many answers. Consider the following example, a naive specification of 
fair \conj{} might require search strategies to produce all sorts of singleton 
lists, but no longer ones, which makes the strategies \emph{incomplete}. 
\NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}
\NOTE[LKC]{I am a bit confused. I assume completeness is a well-known concept 
in the context of logic programming. For example, this paper doesn't cite any 
source when it talks about completeness.

Hemann, Jason, et al. "A small embedding of logic programming with a simple 
complete search." ACM SIGPLAN Notices. Vol. 52. No. 2. ACM, 2016.}

@@

>>>>

The syntax of a programming language should reflect its semantics. When writing 
a \conde{} expression in miniKanren, a programmer would expect all clauses 
share the same chance of being explored, as these clauses are written in 
parallel. The existing search strategy, interleaving \DFSi{}, 
however, prioritize its clauses by the order how they are written down. 
Similarly, when a \conde{} is followed by another goal conjunctively, a 
programmer would expect answers in parallel share the same chance of being 
explored. Again, the answers by \DFSi{} is different from the 
expectation. We have devised three new search strategies that have different 
level of fairness in \disj{} and \conj{}.

@@

\conde intuitively relates its clauses with logical \texttt{or}. And thus an 
unsuspicious beginner would expect each letter to contribute equally to the 
result, as following.

@@

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
A \emph{state} is a collection of constraints. Every answer given by 
miniKanren corresponds to a state. A \emph{search space} is a collection of 
states. And a \emph{goal} is a function from a state to a search space.

% Goals check their input states and outputs possibly extended states. A goal 
% might fail for some inputs, in which case the output search space would be 
% empty.

@@

A more interesting situation is when the first conjunctive goal produces 
infinite many answers. Consider the following example, a naive specification of 
fair \conj{} might require search strategies to produce all sorts of singleton 
lists, but no longer ones, which makes the strategies \emph{incomplete}.

\NOTE[MVC]{incomplete w.r.t. what? where's the definition of incomplete?}

@@

%TODO describe DFSi here
